---
title: "ps_4"
author: "Andres de Loera-Brust"
date: "February 25, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#I begin as always with loading the packages I will use.
library(gt)
library(tidyverse)
library(broom)

#Next I load in the poll data I will be using to answer the questions, adding the column types arguments to my code.
poll <- read_csv(
  file = "ps_4_elections-poll-nc09-3.csv",
  col_types = cols(
    .default = col_character(),
    turnout_scale = col_double(),
    turnout_score = col_double(),
    w_LV = col_double(),
    w_RV = col_double(),
    final_weight = col_double(),
    timestamp = col_datetime(format = "")))

```

## Question 1

There were `r poll %>% filter(response == "Dem") %>% nrow()` respondents who supported the Democratic candidate.

There were `r (filter(poll, response == "Rep") %>% nrow())-(filter(poll, response == "Und") %>% nrow())` more respondents who favored the Republican candidate than who were Undecided.

There are two gender variables (gender and gender_combined). There are `r filter(poll, gender != gender_combined) %>% nrow()` individuals for whom these variables have different values.

There are `r poll %>% filter(race_eth == "White", file_race_black != "White") %>% nrow()` respondents listed as “White” under race_eth who are not listed as “White” under file_race_black.

The first response of Rep came `r as.integer((poll %>% filter(response == "Dem") %>% arrange(timestamp) %>% select(timestamp) %>% slice(1))- (poll %>% filter(response == "Rep") %>% arrange(timestamp) %>% select(timestamp) %>% slice(1)))` minutes (rounded to the nearest minute) before the first response of Dem. In clearer language, the first response of Rep came (roughly) `r as.integer((poll %>% filter(response == "Rep") %>% arrange(timestamp) %>% select(timestamp) %>% slice(1))- (poll %>% filter(response == "Dem") %>% arrange(timestamp) %>% select(timestamp) %>% slice(1)))` minutes after the first response of Dem. 


## Question 2

```{r table} 



```


