---
title: "ps_4"
author: "Andres de Loera-Brust"
date: "February 25, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(gt)
library(tidyverse)
library(broom)

poll <- read_csv(
  file = "ps_4_elections-poll-nc09-3.csv",
  col_types = cols(
    .default = col_character(),
    turnout_scale = col_double(),
    turnout_score = col_double(),
    w_LV = col_double(),
    w_RV = col_double(),
    final_weight = col_double(),
    timestamp = col_datetime(format = "")))

```

## Question 1

There were `r poll %>% filter(response == "Dem") %>% nrow()` respondents who supported the Democratic candidate.

There were `r ` more respondents who favored the Republican candidate than who were Undecided.

There are two gender variables (gender and gender_combined). There are `r ` individuals for whom these variables have different values.

There are `r ` respondents listed as “White” under race_eth who are not listed as “White” under file_race_black.

The first response of Rep came `r ` minutes (rounded to the nearest minute) before the first response of Dem.


## Question 2

```{r} 


```


